Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-04 ProbabilisticCoherence.tex
Notation A changed to B in defintion of probablistic forecast coherence

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}^{\mathbb{R}^m}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$. Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}^{\mathfrak{s}}$.  Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(A)$, where $s(A)$ denotes the image of the set $A\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.  Let the measure $\breve{\nu}$ have the property
  $$
      \breve{\nu}(s(A)) = \nu(A) \quad \forall  A \in \mathscr{F}^{\mathbb{R}^m},
    $$  
  A probabilistic forecast is coherent if uncertainty in $\bm{y_{t+h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}^{\mathfrak{s}},\breve{\nu})$.
\end{definition}

>>>>

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}^{\mathbb{R}^m}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$. Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}^{\mathfrak{s}}$.  Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(B)$, where $s(B)$ denotes the image of the set $B\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.  Let the measure $\breve{\nu}$ have the property
  $$
      \breve{\nu}(s(B)) = \nu(B) \quad \forall  B \in \mathscr{F}^{\mathbb{R}^m},
    $$  
  A probabilistic forecast is coherent if uncertainty in $\bm{y_{t+h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}^{\mathfrak{s}},\breve{\nu})$.
\end{definition}
